The SMT Competition 2015--2018

### 2019-04-14 2018/report/SMT-COMP.tex
Report: Add todo
Report: Pass over unknown analysis

Whilst producing these results we noticed that the description of what constitutes a family had been incorrectly interpreted by the scoring scripts in 2016-2018. After fixing this misinterpretation we note that only a single division winner changes - in 2017 AUFNIRA should have been won by

. As this is in the past we are choosing not to retroactively change the winner (and all tables in this paper reflect the previously published results) but the scripts have been fixed for future iterations of the competition.

\input{table-winners-main-families}
%%%%%%%%%%%%%%%%%
\subsection{What Impact Did Adding Unknowns Have?}

In 2017 the \maintrack ran with benchmarks with unknown status (removing any that had disagreements). An interesting question is to what extent this affected the winners in the \maintrack. Table~\ref{tab:results:unknowns} gives the alternative winners if these benchmarks had not been included.

>>>>

Whilst producing these results we noticed that the description of what constitutes a family had been incorrectly interpreted by the scoring scripts in 2016-2018. After fixing this misinterpretation we note that only a single division winner changes - in 2017 AUFNIRA should have been won by 
\todo{who instead of who?}. As this is in the past we are choosing not to retroactively change the winner (and all tables in this paper reflect the previously published results) but the scripts have been fixed for future iterations of the competition.

\input{table-winners-main-families}
%%%%%%%%%%%%%%%%%
\subsection{What Impact Did Adding Unknowns in the \maintrack Have?}

Until 2016, only benchmarks with known status were used in the \maintrack. In
2016, benchmarks with unknown status were evaluated separately, but not
considered in the overall results of the track.  Since 2017, non-incremental
benchmarks with unknown status were eligible for the \maintrack.
Table~\ref{tab:results:unknowns} shows alternative winners for 2017 and 2018 if
benchmarks with unknown status had not been included.
